Understanding the Socio-Economic Determinants of Voter Behavior: An Analysis of the 2020 U.S. Presidential Election

### 2024-03-16 paper/us_election_2020.qmd
final edits

# Additional data details

@@

posterior_vs_prior(political_preferences1) +
  theme_minimal() +
  theme(legend.position = "bottom") +
  coord_flip()
```

## Credibility Interval {#sec-credibility-interval}

@@

>>>>

@@

posterior_vs_prior(political_preferences1, size = 0.3) +
  theme_minimal() +
  theme(legend.position = "bottom") +
  coord_flip()
```

@@

## Credibility Interval {#sec-credibility-interval}
90% Credibility intervals graph are shown in @fig-modelresults1 and @fig-modelresults2.
